Resource Allocation in an Open RAN System using Network Slicing\vspace{-.1cm}

### 2022-07-08 Journal1/Response3/Response.tex

% % % % % % % % % % % % % % % Reviewer 2 % % % % % % % % % % % % % % % % % % % %
\clearpage
\noindent
\begin{longtable}{|p{.975\textwidth}|}
\hline \hline %\hline \hline \hline
\Centering
\cellcolor{gray!60}
\textbf{Reviewer 2} \\
\hline \hline %\hline \hline \hline
\RaggedRight
\cellcolor{violet!15}
\textbf{\noindent Comments to the Author} ``
The Reviewer would like to thank the authors for their revision of the paper with respect to the comments and suggestions in the previous submission. Whereas the authors have considered parts of the suggestions and improved specific areas of the work, there are still a lot of remaining issues of concern in the current version of the paper. ''\\
\hline
\end{longtable}
\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}
It is our pleasure to thank the reviewer for the careful reading of this manuscript, providing
thoughtful comments, and offering constructive suggestions that strengthened and enhanced its
quality. We hope that the responses provided herein can alleviate the reviewer’s concerns.

\begin{longtable}{|p{0.975\textwidth}|}
\hline \hline
\RaggedRight
\cellcolor{gray!15}
\textbf{\noindent Comment1:} ``While the authors have taken into consideration the Reviewer’s comments about the re-structuring of the Introduction, I am afraid that the current version is not in the adequate state for publication. Initially, the paragraphs of the Introduction have no logical connection among them. It seems that until the Related Literature subsection all paragraphs are disconnected and only introduce concepts. ''\\
\hline
\end{longtable}
\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}
We would like to thank the reviewer for the careful and thorough reading of our manuscript and the thoughtful comment and constructive suggestions that helped us improve the quality of this manuscript and make it more readable. 
We changed the introduction and add it below

%\subsection{State Of The Arts}
Network slicing is a key technology in 5G wireless systems. Specifically, network slicing provides the isolation of network resources into slices, e.g., via core slicing and/or radio access network (RAN) slicing, for serving multiple and heterogeneous service classes [1]–[3]. There are three main service classes in 5G, namely enhanced mobile broadband (eMBB), ultra-reliable low latency communications (URLLC), and massive machine-to-machine communications (mMTC). Depending on their corresponding quality of service (QoS) requirements, each service is assigned to a slice of the network.
For instance, the eMBB service demands high capacity and throughput,  e.g., 8K video streaming and immersive gaming. Meanwhile, the URLLC service, leveraged, e.g., by autonomous vehicles, Tactile Internet, and remote surgery services, is concerned with providing ultra-reliable and low-latency connectivity. Finally, mMTC services require connectivity for a large number of Internet of Things (IoT) devices that transmit small payloads [4]–[6].
%\cite{dogra2020survey,kassab2018coexistence,alsenwi2021intelligent,SL}.}

Unfortunately, the existing radio access network (RAN) architecture still lacks adequate flexibility and openness to manage these demands for various services simultaneously. In view of this, a new RAN paradigm, called open RAN (O-RAN), which is schematically represented in Fig. 1, is introduced to deal with these issues.
%This paper considers several user equipments (UEs) requesting one of these types of services with different QoS in the O-RAN architecture. We want to study RAN slicing technology and the isolation between slices in this system to evaluate the performance of various services.
%This paper aims to design a RAN slicing technology for the O-RAN architecture. 
%O-RAN offers machine learning techniques based on the requirement for an intelligent wireless network for the next generation of RAN systems. The two logical nodes, RIC-Non Real-Time (which is placed in Orchestration and Automation node) and RIC-Near Real-Time, implement the algorithms for network intelligence

A key feature of the O-RAN architecture is that the hardware is disaggregated from the software, leading to network function virtualization (NFV). Additionally, each component is implemented as a virtual network function (VNF), the system function block in NFV, that can be deployed on a virtual machine (VM) or container [7],[8].
As a result, some O-RAN components defined in Section III, such as user plane function (UPF), O-RAN central unit (O-CU), O-RAN distributed unit (O-DU), and RAN intelligent controller (RIC)-near real-time, are virtualized and implemented as VNFs.
\begin{longtable}{|p{0.975\textwidth}|}
\hline \hline
\RaggedRight
\cellcolor{gray!15}
\textbf{\noindent Comment2:} `` Moreover, I find the ORAN explanation in the Introduction very lengthy and unnecessary. I would definitely suggest to move that as a background Section. ''\\
\hline
\end{longtable}
\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}
I would appreciate your comments to enhance and clarify this section of the paper. I moved the background as a section.
\begin{longtable}{|p{0.975\textwidth}|}
\hline \hline
\RaggedRight
\cellcolor{gray!15}
\textbf{\noindent Comment3:} `` Furthermore, it is surprising how the Introduction does not contain a single research challenge. Why is the problem relevant at all? Why do you even need to study this problem and why is it hard to solve? ''\\
\hline
\end{longtable}
\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}
We add the motivation subsection and answer these questions in it. Below we rewrite this section.

The problem of finding the optimal resource allocation, independently of the specific RAN technology, is vital for reducing the cost of the system and improving the QoS of the user equipments (UEs). In case of 5G systems, there are many related significant challenges such as interference alignment, limited capacity of fronthaul links, energy restrictions on virtual machines, etc [2],[9],[10].

Many studies have investigated resource allocation in cloud RAN (C-RAN) by considering the power, data rate and delay limitations of a single service. Due to the contemporary need to serve services with different QoS simultaneously, e.g., as in 5G and beyond, this architectural model is inefficient. In this regard, the O-RAN architecture has emerged as a flexible, layered, and modular design architecture that can simultaneously support multiple services at a lower cost. Nevertheless, RAN slicing in the O-RAN architecture still faces various challenges. 
One of the fundamental problems lies in attaining a balance between different services with different QoS, resource requirements, and priorities [1],[11]–[13].  
%\textcolor{MidnightBlue}{Since 5G defines different services with different QoS, we need to analyze the resource allocation for each 5G service, using RAN slicing to guarantee the QoS for them.
%Consequently, we consider the O-RAN architecture, the new generation of RAN architecture that can implement RAN slicing for different 5G services. 
%We investigate the problem of resource allocation in the O-RAN architecture for the three services defined in the 5G with different QoS serving simultaneously.}

The purpose of this paper is to design a system in the O-RAN architecture to support the three types of 5G services, namely, eMBB, URLLC, and mMTC via network slicing and resource allocation. Specifically, we aim to maximize the total achievable data rate and satisfy the minimum achievable data rate for eMBB services while meeting the URLLC requirements in the presence of numerous low-power IoT devices.
\begin{longtable}{|p{0.975\textwidth}|}
\hline \hline
\RaggedRight
\cellcolor{gray!15}
\textbf{\noindent Comment4:} `` In turn, in the main contributions subsection, the initial sentences of almost all contribution paragraphs cannot be considered as contributions. For instance:

1) “We have carefully considered the processing delay and the VNF resources needed for the slice compared to other papers.”
2) “ Different services need to consider varying QoS conditions, including delay, power, and throughput.”
3) “The main problem is mixed-integer non-linear programming that is extremely difficult to solve.”
''\\
\hline
\end{longtable}
\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}
We removed these sentences and rewrite the main contribution. Below we write the modified main contribution.

This paper aims to optimize the resource utilization of a downlink O-RAN system to develop an isolated network slicing outline for the three 5G service classes.
We use mathematical methods to decompose and convexify the problem and solve it using hierarchical algorithms.
%Our paper focuses on the multi-service resource management of the RAN slicing in an open and flexible O-RAN architecture.}
%In this paper, as depicted in Figure \ref{fig:c11}, the downlink of the O-RAN system is studied.
 The main contributions of this paper are summarized as follows:
\begin{itemize}
\item We examine the problem of radio resource allocation and VNF activation within the O-RAN architecture.
Based on the three types of 5G service classes, i.e., eMBB, URLLC and mMTC, and their corresponding QoS requirements and service priorities, we formulate a problem for allocating baseband resources such as power, physical resource blocks (PRBs), O-RUs, and activating VNFs to maximize the weighted throughput of the O-RAN.
\item We propose a two-step resource management algorithm for solving the optimization problem.
In the first step, we reformulate and simplify the problem so as to find an upper and lower bound for the number of activated VNFs. Moreover, we use the Lagrangian function and Karush-Kuhn-Tucker (KKT) conditions to obtain the optimal power and PRB allocation. In the second step, the problem of O-RU association is converted to a multiple knapsack problem and solved by a greedy algorithm.
\item We provide insights into the complexity of the proposed algorithms and demonstrate their convergence. Additionally, we analyze the feasibility region of our problem and introduce a fast algorithm to check its feasibility numerically.
\item We show via numerical results that the proposed algorithm outperforms two baseline schemes, in terms of achievable data rate and mean total delay. Remarkably, the proposed algorithm performs close to the optimal solution in low-interference conditions.
\end{itemize}

\begin{longtable}{|p{0.975\textwidth}|}
\hline \hline
\RaggedRight
\cellcolor{gray!15}
\textbf{\noindent Comment5:} `` In a similar fashion, the authors have not considered the Reviewer’s suggestion to move the Related Work as a separate Section in order to improve the flow and clarity of the Introduction. ''\\
\hline
\end{longtable}
\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}
Thank you for this comment. We moved the background from sub-section to the section part and modified it as below.

\begin{longtable}{|p{0.975\textwidth}|}
\hline \hline
\RaggedRight
\cellcolor{gray!15}
\textbf{\noindent Comment6:} `` Regarding the Reviewer’s comment with respect to the network slice management, whereas the authors have introduced the 4 stages of the life cycle of a network slice, the connection to their approach is very vague. It is still not clear how this process is achieved and how it is linked to their method. I was expecting at least a connection or introduction to Fig.1 where the system is shown. Additionally, more information with respect to the interaction with the system would have been required in that regard. ''\\
\hline
\end{longtable}
\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}
We add the following part to the slice management section.

### 2022-07-08 Journal1/paper5TNSM/pr.tex
add revise

The next radio access network (RAN) generation, open RAN (O-RAN), aims to enable more flexibility and openness, including efficient service slicing, and to lower the operational costs in 5G and beyond wireless networks. Nevertheless, strictly satisfying quality-of-service requirements, while establishing priorities and promoting balance between the significantly heterogeneous services remains as key research problem.
In this paper, we study the problem of service-aware baseband resource allocation and virtual network function (VNF) activation in O-RAN systems using network slicing.

@@

Open Radio Access Network (O-RAN), Virtual Network Function (VNF), Network Slicing, Knapsack Problem, Greedy Algorithm, Karush-Kuhn-Tucker (KKT) Conditions.

@@

\textcolor{MidnightBlue}{A key feature of the O-RAN architecture is that the hardware is disaggregated from the software, leading to network function virtualization (NFV). Additionally, each component is implemented as a virtual network function (VNF), the system function block in NFV, that can be deployed on a virtual machine (VM) or container \cite{mijumbi2015network, luo2020online}.}
\textcolor{MidnightBlue}{As a result, some O-RAN components defined in Section \ref{BG}, such as user plane function (UPF), O-RAN central unit (O-CU), O-RAN distributed unit (O-DU), and RAN intelligent controller (RIC)-near real-time, are virtualized and implemented as VNFs.}

\begin{figure}
  \centering
  \captionsetup{justification=centering}
    \includegraphics[scale = 0.39]{finalDraw1.pdf}
    %\includegraphics[width=9.cm,height=6.2cm]{finalDraw1.pdf}
    %\includegraphics[width=\textwidth]{finalDraw.pdf}
  \caption{Network sliced O-RAN system}
  \label{fig:c11}
\end{figure}
\subsection{Motivation}
\textcolor{MidnightBlue}{The problem of finding the optimal resource allocation, independently of the specific RAN technology, is vital for reducing the cost of the system and improving the QoS of the user equipments (UEs). In case of 5G systems, there are many related significant challenges such as interference alignment, limited capacity of fronthaul links, energy restrictions on virtual machines, etc \cite{lee2018dynamic,SystemCostMinimization, setayesh2020joint}.}

@@

\textcolor{MidnightBlue}{This paper aims to optimize the resource utilization of a downlink O-RAN system to develop an isolated network slicing outline for the three 5G service classes.
We use mathematical methods to decompose and convexify the problem and solve it using hierarchical algorithms.}
%Our paper focuses on the multi-service resource management of the RAN slicing in an open and flexible O-RAN architecture.}
%In this paper, as depicted in Figure \ref{fig:c11}, the downlink of the O-RAN system is studied.
 The main contributions of this paper are summarized as follows:
\begin{itemize}
\item \textcolor{MidnightBlue}{We examine the problem of radio resource allocation and VNF activation within the O-RAN architecture.
Based on the three types of 5G service classes, i.e., eMBB, URLLC and mMTC, and their corresponding QoS requirements and service priorities, we formulate a problem for allocating baseband resources such as power, physical resource blocks (PRBs), O-RUs, and activating VNFs to maximize the weighted throughput of the O-RAN.}
\item \textcolor{MidnightBlue}{We propose a two-step resource management algorithm for solving the optimization problem.
In the first step, we reformulate and simplify the problem so as to find an upper and lower bound for the number of activated VNFs. Moreover, we use the Lagrangian function and Karush-Kuhn-Tucker (KKT) conditions to obtain the optimal power and PRB allocation. In the second step, the problem of O-RU association is converted to a multiple knapsack problem and solved by a greedy algorithm.}
\item \textcolor{MidnightBlue}{We provide insights into the complexity of the proposed algorithms and demonstrate their convergence. Additionally, we analyze the feasibility region of our problem and introduce a fast algorithm to check its feasibility numerically.}
\item \textcolor{MidnightBlue}{We show via numerical results that the proposed algorithm outperforms two baseline schemes, in terms of achievable data rate. Remarkably, the proposed algorithm performs close to the optimal solution in low-interference conditions.}
\end{itemize}

The rest of this paper is organized as follows.
Relevant literature related to our work is discussed in Section~\ref{RL}, while Section~\ref{BG} briefly overviews the O-RAN architecture.
The system model and the problem formulation are described in Section \ref{systemmodel}. The details of our proposed resource management algorithm are introduced in Section \ref{proAlg}. In Section \ref{NE}, numerical results are provided to evaluate the performance of the proposed algorithm. Finally, Section \ref{conc} concludes the paper.
\begin{table}[H]
 \caption {List of Acronyms} \label{table:1a}
 \begin{center}
 \scalebox{1}{
  \begin{tabular}{c  c }
  \toprule
\textbf{Acronym} & \textbf{Definition} \\ [0.5ex]
   \toprule
  VNF & virtual network function\\[.5ex]

@@

  UE &  user equipment \\ [.5ex]

  KKT &  Karush-Kuhn-Tucker \\ [.5ex]
 \toprule
 \end{tabular}}
 \end{center}
 \end{table}
\section{Related Literature}\label{RL}
The problem of network slicing in multi-tenant cellular networks has received significant attention recently, e.g.,  \cite{feng2020dynamic,lee2018dynamic,lee2016new}.
In \cite{lee2018dynamic}, dynamic network slicing in heterogeneous C-RAN (H-CRAN) is considered in two levels. The higher level manages user acceptance control, radio remote head (RRH) association, and the allocation of BBU capacity. Meanwhile, the allocation of power and physical resource blocks (PRB) is performed at the lower level.
In \cite{xiang2020realization}, RAN slicing is considered for the fog RAN (F-RAN) system, and executed using deep reinforcement learning algorithm. In \cite{elayoubi20195g,d2020toward}, the implementation of RAN level slicing is discussed for the mobile network operator.

Multiplexing eMBB and URLLC services on the same RAN is particularly challenging, which has motivated some recent works.
In \cite{setayesh2020joint}, the problem of resource allocation in the coexistence of URLLC and eMBB services is considered to maximize the sum rate by ensuring that each user's traffic load demand is met and the slice isolation is guaranteed.
In \cite{yang2020should} a RAN slicing is considered in the coordinated multipoint system for eMBB and URLLC services to guarantee their QoS and reliability of URLLC. Moreover, \cite{saggese2021power} investigates the minimization of the system's power in the downlink RAN slicing of eMBB and URLLC services using non-orthogonal multiple access technique.
In \cite{alsenwi2021intelligent}, the problem of resource allocation for joint eMBB and URLLC services is formulated and solved by deep reinforcement learning.
% In \cite{korrai2020ran}, the authors proposed to allocate RAN resources for the network slicing system in the coexistence of eMBB and URLLC services. The system guarantees latency, service rate, and reliability maintenance.

@@

\section{Background}\label{BG}
\textcolor{MidnightBlue}{The Open Radio Access Network (O-RAN) is an appropriate alternative to the next generation of radio access networks due to its flexible operations, openness, lower operational costs, and intelligence.}

O-RAN is driven by two pillars of openness and RAN intelligence as the next generation of radio access networks. O-RAN was developed to jointly benefit the advantages of virtual RAN (vRAN) and cloud RAN (C-RAN). With RAN virtualization, operators can improve flexibility, reduce capital expenditures (CAPEX) and operating expenses (OPEX), and add new capabilities to the network more quickly. The C-RAN architecture divides the radio remote head (RRH) and baseband unit (BBU) into two major parts. Several distributed RRHs can be connected to a centralized BBU, called BBU-pool \cite{han2019research}. Unlike C-RAN, O-RAN separates RAN into three different units, namely Radio Unit (O-RU), Distributed Unit (O-DU), and Central Unit (O-CU).

O-RU is a logical node that contains RF and lowers PHY. Moreover, the O-DU expresses a logical node with higher PHY, MAC, and RLC.
In addition, the O-CU contains two parts: the O-CU user plane (O-CU-UP) and the O-CU control plane (O-CU-CP). O-CU-UP hosts PDCP-UP and SDAP, and O-CU-CP hosts PDCP-CP and RRC.
O-DU and O-CU are connected via an open and well-defined interface $F_1$.
Moreover, O-DU is connected to a radio unit (O-RU) with an open fronthaul interface.
The architecture of O-RAN contains other principal logical nodes called Orchestration and Automation, RAN Intelligent Controller (RIC)- Near Real-Time, and O-Cloud\cite{gavrilovska2020cloud,niknam2020intelligent,kazemifard2021minimum,both2021system,ORANArch,ORANML,lin2021toward}. 
%\begin{table}[H]
% \caption {List OF Notation} \label{table:1a}
% \begin{center}
% \scalebox{0.8}{
%  \begin{tabular}{||c | c ||}
%  \hline
%Notation & Description \\ [0.5ex]
%  \hline\hline
%  $S$ & Total number of slices\\
%  \hline
%  $S1$ & Number of eMBB slices  \\
%  \hline
% $S2$ & Number of URLLC slices  \\
%  \hline
%  $S3$ & Number of mMTC slices \\
%  \hline
%   $\bar{K}_s$ & pre-allocated PRB to each slice \\
%  \hline
%  PRB &  Physical Resource Block \\
%  \hline
%  eMBB & enhanced Mobile BroadBand \\
%  \hline
%  URLLC  & Ultra-Reliable Low Latency Communication \\
%   \hline
%  mMTC &  massive Machine-To-Machine Communications \\
%  \hline
%  O-RU &  O-RAN Radio Unit \\
%  \hline
%   O-DU &  O-RAN Distributed Unit \\ [.5ex]
%  \hline
%   O-CU &  O-RAN Central Unit \\ [.5ex]
%  \hline
%  UPF &  User Plane Function \\ [.5ex]
%  \hline
% \end{tabular}}
% \end{center}
% \end{table}
\section{System Model and Problem Formulation}\label{systemmodel}
In this section, we describe the downlink system in the O-RAN architecture using RAN slicing as depicted in Figure \ref{fig:c11}.
Firstly, we present the system model. Then, we obtain achievable data rates, power of O-RU, and the fronthaul capacity for the downlink (DL) of the o-ran system. Afterward, we discuss the mean delay and the power of VNFs.
Finally, the main problem is expressed.
\subsection{System Model}
Assume, there are three service types including eMBB, URLLC, and mMTC which support different applications. Accordingly, there are $S_1$ slices for the first service type (eMBB), $S_2$ slices for the second service type (URLLC), and $S_3$ slices for the third service type (mMTC).
Therefore, there are $S$ pre-allocated slices serving these $S$ services ($S = S_1 + S_2 + S_3$);
Hence, each service request $s\in \{1,\ldots,S\}$ is served by its corresponding slice. So we have
$\{1,2,...,S_1\}$ set of eMBB service instances, $\{1,2,...,S_2\}$ set of URLLC service instances, and
$\{1,2,...,S_3\}$ set of mMTC service instances.
Each Service $s_j\in \{1,2,...,S_j\} $ consists of $U_{s_j}$ requests from  single-antenna UEs which require certain level of QoS. We notice that $j \in \{1,2,3\}$ indicates the service type.
There are different application requests which fall into one of these service categories. Each application request requires a specific QoS. Based on the application and QoS request, UE may be admitted and allocated to the resources.

Each pre-allocated slice contains reserved VNFs for the three logical nodes:
\begin{itemize}
\item The MAC/RLC functions in the O-DU logical node
\item The PDCP/SDAP functions in the O-CU-UP logical node
\item The UPF logical node
\end{itemize}
Each slice $s \in \{1,2,...,S \}$, consists of  $M_s^{d}$ VNFs for the processing of O-DU, $M_s^{c}$ VNFs for the processing of O-CU-UP and $M_s^{u}$ VNFs for the processing of UPF.
The VNFs of O-DU, O-CU-UP, and UPF are interconnected, defined as the Service Function Chain (SFC) in the O-RAN system. Also, each VNF instance runs on a virtual machine (VM) that uses resources from the data centers.

%All $K$ PRBs can be assigned to all UEs in each service.
Assume there are $K$ physical resource blocks (PRBs) in this system. Suppose each slice $s$ consists of $\bar{K}_s$ pre-allocated virtual resource blocks that are mapped to Physical Resource Blocks (PRBs). Therefore, we have $\sum_s \bar{K}_s \leq K$.

In addition, there are $R$ multi-antenna O-RUs that are shared between slices. O-RU $r \in \{1,2,...,R \}$ has $J$ antennas for transmitting and receiving data. Also $\mathcal{R} = \{ r \ | \ r\in 1,2,...,R \}$ depicts the set of O-RUs. Moreover, all O-RUs have access to all PRBs.

>>>>

The next radio access network (RAN) generation, open RAN (O-RAN), aims to enable more flexibility and openness, including efficient service slicing, and to lower the operational costs in 5G and beyond wireless networks. Nevertheless, strictly satisfying quality-of-service requirements, while establishing priorities and promoting balance between the significantly heterogeneous services, remains as a key research problem.
In this paper, we study the service-aware baseband resource allocation and virtual network function (VNF) activation in O-RAN systems using network slicing.

@@

open radio access network (O-RAN), virtual network function (VNF), network slicing, knapsack problem, greedy algorithm, Karush-Kuhn-Tucker (KKT) Conditions.

@@

\textcolor{MidnightBlue}{A key feature of the O-RAN architecture is that the hardware is disaggregated from the software, leading to network function virtualization (NFV). Additionally, each component is implemented as a virtual network function (VNF), the system function block in NFV, that can be deployed on a virtual machine (VM) or container \cite{mijumbi2015network}.}
\textcolor{MidnightBlue}{As a result, some O-RAN components defined in Section \ref{BG}, such as user plane function (UPF), O-RAN central unit (O-CU), O-RAN distributed unit (O-DU), and RAN intelligent controller (RIC)-near real-time, are virtualized and implemented as VNFs.}

\begin{figure}
  \centering
  \captionsetup{justification=centering}
    \includegraphics[scale = 0.36]{finalDraw1.pdf}
    %\includegraphics[width=9.cm,height=6.2cm]{finalDraw1.pdf}
    %\includegraphics[width=\textwidth]{finalDraw.pdf}
  \caption{Network sliced O-RAN system}
  \label{fig:c11}
\end{figure}
\subsection{Motivation}
\textcolor{MidnightBlue}{The problem of finding the optimal resource allocation, independently of the specific RAN technology, is vital for reducing the cost of the system and improving the QoS of the user equipments (UEs). In case of 5G systems, there are many related significant challenges such as interference alignment, limited capacity of fronthaul links, energy restrictions on virtual machines, etc \cite{lee2018dynamic,SystemCostMinimization, setayesh2020joint}.}

@@

\textcolor{MidnightBlue}{This paper aims to optimize the resource utilization of a downlink O-RAN system to develop an isolated network slicing outline for the three 5G service classes.
We use mathematical methods to decompose and convexify the problem and solve it using hierarchical algorithms.}
%Our paper focuses on the multi-service resource management of the RAN slicing in an open and flexible O-RAN architecture.}
%In this paper, as depicted in Figure \ref{fig:c11}, the downlink of the O-RAN system is studied.
 The main contributions of this paper are summarized as follows:
\begin{itemize}
\item \textcolor{MidnightBlue}{We examine the problem of radio resource allocation and VNF activation within the O-RAN architecture.
Based on the three types of 5G service classes, i.e., eMBB, URLLC and mMTC, and their corresponding QoS requirements and service priorities, we formulate a problem for allocating baseband resources such as power, physical resource blocks (PRBs), O-RUs, and activating VNFs to maximize the weighted throughput of the O-RAN.}
\item \textcolor{MidnightBlue}{We propose a two-step resource management algorithm for solving the optimization problem.
In the first step, we reformulate and simplify the problem so as to find an upper and lower bound for the number of activated VNFs. Moreover, we use the Lagrangian function and Karush-Kuhn-Tucker (KKT) conditions to obtain the optimal power and PRB allocation. In the second step, the problem of O-RU association is converted to a multiple knapsack problem and solved by a greedy algorithm.}
\item \textcolor{MidnightBlue}{We provide insights into the complexity of the proposed algorithms and demonstrate their convergence. Additionally, we analyze the feasibility region of the problem under consideration and introduce a fast algorithm to check its feasibility numerically.}
\item \textcolor{MidnightBlue}{We show via numerical results that the proposed algorithm outperforms two baseline schemes in terms of achievable data rate and mean total delay. Remarkably, the proposed algorithm performs close to the optimal solution in low-interference conditions.}
\end{itemize}

Table \ref{table:11a} lists the acronyms used throughout this paper, which is organized as follows.
Relevant literature related to our work is discussed in Section~\ref{RL}, while Section~\ref{BG} briefly overviews the O-RAN architecture.
The system model and the problem formulation are described in Section \ref{systemmodel}. The details of our proposed resource management algorithm are introduced in Section \ref{proAlg}. In Section \ref{NE}, numerical results are provided to evaluate the performance of the proposed algorithm. Finally, Section \ref{conc} concludes the paper.

\begin{table}[H]
\vspace*{-0em}
 \caption {List of Acronyms} \label{table:11a}
 \vspace*{-1em}
 \begin{center}
 \scalebox{1}{
  \begin{tabular}{l  l }
  \toprule
  \vspace*{-0.2em}
\textbf{Acronym} & \textbf{Definition} \\ [0.5ex]
   \toprule
  VNF & virtual network function\\[.5ex]

@@

  UE &  user equipment \\ [.5ex]
  SINR & signal-to-noise-plus-interference ratio \\ [.5ex]
  CAPEX & capital expenditures  \\ [.5ex]
  OPEX & operating expenses  \\ [.5ex]

  KKT &  Karush-Kuhn-Tucker \\ [.5ex]
 \toprule
 \end{tabular}}
 \end{center}
 \end{table}
 \vspace*{-2em}
\section{Related Literature}\label{RL}
The network slicing problem in multi-tenant cellular networks has received significant attention recently, e.g.,  \cite{feng2020dynamic,lee2018dynamic,lee2016new}.
In \cite{lee2018dynamic}, dynamic network slicing in heterogeneous C-RAN (H-CRAN) is considered in two levels. The higher level manages user acceptance control, radio remote head (RRH) association, and the allocation of BBU capacity. Meanwhile, the allocation of power and PRB is performed at the lower level.
In \cite{xiang2020realization}, RAN slicing is considered for the fog RAN (F-RAN) system, and executed using deep reinforcement learning. In \cite{elayoubi20195g,d2020toward}, the implementation of RAN level slicing is discussed among multiple mobile network operators with the specific physical network resources infrastructure.

Multiplexing eMBB and URLLC services on the same RAN is particularly challenging, which has motivated some recent works.
\textcolor{MidnightBlue}{In \cite{setayesh2020joint}, the sum rate of the eMBB, and URLLC, is optimized by ensuring that each user's traffic load demand is met and the slice isolation is guaranteed, thus promoting an amicable service coexistence.
In \cite{yang2020should}, a RAN slicing is considered in a coordinated multipoint system to guarantee the QoS requirements of eMBB and URLLC services.} Moreover, \cite{saggese2021power} investigates the minimization of the system's power for the  RAN slicing of eMBB and URLLC downlink services using non-orthogonal multiple access techniques.
In \cite{alsenwi2021intelligent}, the problem of resource allocation for the coexistence of eMBB and URLLC services is formulated and solved by deep reinforcement learning.
% In \cite{korrai2020ran}, the authors proposed to allocate RAN resources for the network slicing system in the coexistence of eMBB and URLLC services. The system guarantees latency, service rate, and reliability maintenance.

@@

\section{Background}\label{BG}
\textcolor{MidnightBlue}{O-RAN is an appropriate alternative to the next generation of radio access networks due to its flexible operations, openness, lower operational costs, and intelligence. O-RAN was developed to jointly benefit from the advantages of virtual RAN (vRAN) and cloud RAN (C-RAN).} With RAN virtualization, operators can improve flexibility, reduce capital expenditures (CAPEX) and operating expenses (OPEX), and add new capabilities to the network more quickly. The C-RAN architecture divides the RAN into two major parts: the radio remote head (RRH) and the baseband unit (BBU). Several distributed RRHs can be connected to a centralized BBU, called BBU-pool \cite{han2019research}. Unlike C-RAN, O-RAN separates RAN into three different units, namely Radio Unit (O-RU), Distributed Unit (O-DU), and Central Unit (O-CU).
\textcolor{MidnightBlue}{ Most real-time baseband processing is performed in the O-DU layer, while mostly non-real-time baseband processing is executed in the O-CU layer. Therefore, the three-layer O-RAN architecture can achieve lower cost and power consumption benefits than the two-layer C-RAN architecture.}

As shown in Fig. \ref{fig:c11}, O-RU is a logical node that contains RF and low PHY. Moreover, the O-DU expresses a logical node with higher PHY, MAC, and RLC.
In addition, the O-CU contains two parts: the O-CU user plane (O-CU-UP) and the O-CU control plane (O-CU-CP). O-CU-UP hosts PDCP-UP and SDAP, and O-CU-CP hosts PDCP-CP and RRC.
O-DU and O-CU are connected via an open and well-defined interface $F_1$.
Moreover, O-DU is connected to a radio unit (O-RU) with an open fronthaul interface.
The O-RAN architecture contains other principal logical nodes called Orchestration and Automation, RAN Intelligent Controller (RIC)- Near Real-Time, and O-Cloud\cite{gavrilovska2020cloud,niknam2020intelligent,kazemifard2021minimum,both2021system,ORANArch,ORANML,lin2021toward}. 
%\begin{table}[H]
% \caption {List OF Notation} \label{table:1a}
% \begin{center}
% \scalebox{0.8}{
%  \begin{tabular}{||c | c ||}
%  \hline
%Notation & Description \\ [0.5ex]
%  \hline\hline
%  $S$ & Total number of slices\\
%  \hline
%  $S1$ & Number of eMBB slices  \\
%  \hline
% $S2$ & Number of URLLC slices  \\
%  \hline
%  $S3$ & Number of mMTC slices \\
%  \hline
%   $\bar{K}_s$ & pre-allocated PRB to each slice \\
%  \hline
%  PRB &  Physical Resource Block \\
%  \hline
%  eMBB & enhanced Mobile BroadBand \\
%  \hline
%  URLLC  & Ultra-Reliable Low Latency Communication \\
%   \hline
%  mMTC &  massive Machine-To-Machine Communications \\
%  \hline
%  O-RU &  O-RAN Radio Unit \\
%  \hline
%   O-DU &  O-RAN Distributed Unit \\ [.5ex]
%  \hline
%   O-CU &  O-RAN Central Unit \\ [.5ex]
%  \hline
%  UPF &  User Plane Function \\ [.5ex]
%  \hline
% \end{tabular}}
% \end{center}
% \end{table}
\section{System Model and Problem Formulation}\label{systemmodel}
We consider a downlink (DL) , and an O-RAN architecture using RAN slicing as depicted in Fig. \ref{fig:c11}.
In this section, we present the system model, derive the achievable data rates, power of O-RU, and the fronthaul capacity  of the O-RAN system. Moreover, we discuss the mean delay and the power of VNFs, and formulate the main problem under consideration.
\subsection{System Model}
Assume, there are three service types: eMBB, URLLC, and mMTC, which support different applications. Accordingly, there are $S_1$ slices for the first service type (eMBB), $S_2$ slices for the second service type (URLLC), and $S_3$ slices for the third service type (mMTC).
Therefore, there are $S = S_1 + S_2 + S_3$ pre-allocated slices serving these services.
Moreover, each service request $s\in \{1,\ldots,S\}$ is served by its corresponding slice. So we have the set
$\{1,2,...,S_1\}$ of eMBB service instances, the set $\{1,2,...,S_2\}$ of URLLC service instances, and the set
$\{1,2,...,S_3\}$ of mMTC service instances.
Each Service $s_j\in \{1,2,...,S_j\} $ consists of $U_{s_j}$ requests from  single-antenna UEs requiring certain level of QoS. Notice that $j \in \{1,2,3\}$ indicates the service type.
Based on the application and QoS request, UE may be admitted and allocated to the resources.

Each pre-allocated slice contains reserved VNFs for the three logical nodes:
\begin{itemize}
\item MAC/RLC functions in the O-DU logical node
\item PDCP/SDAP functions in the O-CU-UP logical node
\item UPF logical node
\end{itemize}
Each slice $s \in \{1,2,...,S \}$, consists of  $M_s^{d}$ VNFs for the processing of O-DU, $M_s^{c}$ VNFs for the processing of O-CU-UP, and $M_s^{u}$ VNFs for the processing of UPF.
The VNFs of O-DU, O-CU-UP, and UPF are interconnected, which is defined as the service function chain in the O-RAN system. Also, each VNF instance runs on a virtual machine VM that uses resources from the data centers.

%All $K$ PRBs can be assigned to all UEs in each service.
Assume there are $K$ PRBs in this system. Suppose each slice $s$ consists of $\bar{K}_s$ pre-allocated virtual resource blocks that are mapped to PRBs. Therefore, we have $\sum_s \bar{K}_s \leq K$.
In addition, there are $R$ multi-antenna O-RUs that are shared between the slices. Specifically, the O-RU $r \in \mathcal{R}=\{1,2,...,R \}$ has $J$ antennas for transmitting and receiving data. Moreover, all O-RUs have access to all PRBs.
